More on the Slavnov products of spin chains, KP hierarchy tau and Baker-Akhiezer functions

### 2025-05-16 draft.tex
finish section 3 dot 1

Puttting all these facts together, we can write the
expression~(\ref{eq:scalar-prod}) as
\begin{equation}
  \sum_{k=1}^{n+1} L_{jk} \bm{\zeta}_k  = 
  \Lambda(u_j; \bar{v}) \bm{\zeta}_j\quad \Rightarrow \quad
  \sum_{k=1}^{n+1} M_{jk} \bm{\zeta}_k = 0 \; ,
\end{equation}
where we have defined the coefficients
\begin{equation}
  M_{jk} = L_{jk} - \delta_{jk}\Lambda(u_j; \bm{v})\; . 
\end{equation}
In simple terms, this expression shows that the Slavnov products
satisfy a linear system.  We can write this system in a matrix form as
\begin{equation}
\bm{M} \bm{\zeta} = 
  \left(\bm{L} - \bm{\Lambda} \right) \bm{\zeta} = \bm{0}\; ,
\end{equation}
where
\begin{subequations}
  \begin{equation}
    \bm{L} = 
 \begin{pmatrix}
   L_{1,1} & \cdots & L_{1,n+1}\\
   L_{2,1} & \cdots & L_{2,n+1}\\
   \vdots & \vdots & \vdots\\
   L_{n+1, 1} & \cdots & L_{n+1, n+1}\\
 \end{pmatrix}  \quad , \quad
    \bm{\Lambda} = \mathrm{diag}(\Lambda_1, \Lambda_2, \dots, \Lambda_{n+1})
\end{equation}
with \(\Lambda_j \equiv \Lambda(u_j; \bm{v})\), and
\begin{equation}
  \bm{\zeta} = (\bm{\zeta}_1, \dots , \bm{\zeta}_{n+1})^T\qquad \, 
  \bm{0} = (0, \dots , 0)^T\; .
\end{equation}
\end{subequations}
This completes the proof of their proposition. 
 \qed

@@

\todo{15/05}
\begin{remark}
  In~\cite{Segal:1985aga, Kharchev:1991cy, Alexandrov:2014cwa}, the
  authors have explored a family of functions \(\{ \phi_i\}_{i=1}^n\)
  that forms a basis vector because they parametrize points in a
  Grassmannian space. These functions are also useful in the
  definition of the Baker-Akhiezer function. The important aspect for
  us is that the functions \(\Omega_j\) relevant for our discussion do
  not belong to the class discussed in the references above.
  Therefore, we need to explore their properties and the
  Baker-Akhiezer functions relevant to our present discussion.
\end{remark}

\begin{remark}
  Reduction of a multicomponent KP Hierarchy
  It is interesting to observe that we have an array of tau functions ...
\end{remark}

>>>>

Puttting all these facts together, we can write the
expression~(\ref{eq:scalar-prod}) as
\begin{equation}
  \sum_{k=1}^{n+1} L_{jk} \bm{\zeta}_k  = 
  \Lambda(u_j; \bar{v}) \bm{\zeta}_j\quad \Rightarrow \quad
  \sum_{k=1}^{n+1} M_{jk} \bm{\zeta}_k = 0 \; ,
\end{equation}
where we have defined the coefficients
\begin{equation}
  M_{jk} = L_{jk} - \delta_{jk}\Lambda(u_j; \bm{v})\; . 
\end{equation}
In simple terms, this expression shows that the Slavnov products
satisfy a linear system.  We can write this system in a matrix form as
\begin{equation}
\label{eq:linear-system}
\bm{M} \bm{\zeta} = 
  \left(\bm{L} - \bm{\Lambda} \right) \bm{\zeta} = \bm{0}\; ,
\end{equation}
where
\begin{subequations}
  \begin{equation}
    \bm{L} = 
 \begin{pmatrix}
   L_{1,1} & \cdots & L_{1,n+1}\\
   L_{2,1} & \cdots & L_{2,n+1}\\
   \vdots & \vdots & \vdots\\
   L_{n+1, 1} & \cdots & L_{n+1, n+1}\\
 \end{pmatrix}  \quad , \quad
    \bm{\Lambda} = \mathrm{diag}(\Lambda_1, \Lambda_2, \dots, \Lambda_{n+1})
\end{equation}
with \(\Lambda_j \equiv \Lambda(u_j; \bm{v})\), and
\begin{equation}
  \bm{\zeta} = (\bm{\zeta}_1, \dots , \bm{\zeta}_{n+1})^T\qquad \, 
  \bm{0} = (0, \dots , 0)^T\; .
\end{equation}
\end{subequations}
This completes the proof of their proposition. 
 \qed

@@

In~\cite{Segal:1985aga, Kharchev:1991cy, Alexandrov:2014cwa}, the
authors explored a family of functions \(\{ \phi_i\}_{i=1}^n\) that
parametrize points in a Grassmannian space. These functions also play
an important role in the definition of the Baker-Akhiezer
functions. However, the asymptotic behavior of the functions
\(\Omega_j\), which are relevant to our discussion, indicates that
they do not belong to the class considered in the references above.
Therefore, we must investigate their properties and the corresponding
Baker-Akhiezer functions specific to our discussion.  We begin this
analysis below.

Given that each function \(\bm{\tau}^{(\ell)}(\bm{z}^{(\ell)}, \bm{v})\), for
\(\ell = 1, \dots, n+1\), is a distinct but related tau function, one
can define a vector
\begin{equation}
  \bm{T}(\bm{Z}, \bm{v}) = 
\begin{bmatrix}
\bm{\tau}^{(1)}(\bm{z}^{(1)}, \bm{v}) \\ 
\bm{\tau}^{(2)}(\bm{z}^{(2)}, \bm{v}) \\ 
\vdots \\ 
\bm{\tau}^{(n+1)}(\bm{z}^{(n+1)}, \bm{v})
\end{bmatrix}
\end{equation}
where \(\bm{Z} = (\bm{z}^{(1)}, \bm{z}^{(2)}, \dots,
\bm{z}^{(n+1)})\). This is a vector of tau functions of the KP
hierarchy. This observation suggests that there is, in fact, an
underlying multicomponent KP hierarchy in this context, and that the
linear system~(\ref{eq:linear-system}), which we can write as
\begin{equation}
\left( \bm{L} - \bm{\Lambda} \right) \bm{T} = \bm{0},
\end{equation}
defines a reduction of this multicomponent KP hierarchy. This
reduction ultimately describes constraints that relate the different
sets of parameters \(\bm{z}^{(\ell)}\).  We have not explored this
idea in this work, but we hope to return to this problem in future
publications.
\todo{16/05}
